---
title: "Run Targets - Northern Water and Cache La Poudre Pipeline"
author: "ROSSyndicate"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

# Purpose

This script loads all necessary packages to run the {targets} pipeline and then
runs it! This pipeline organizes the location and polygon information for the NW
and CLP projects (group a), collates the RS pulls (group c, the RS pulls are 
currently completed in the Landsat-C2-SRST repository, nw-poudre-historical 
branch and nw-er3z21-historical), calculates handoff coefficients (group d),
applies handoff coefficients (group e), then separates the NW and CLP data and 
saves the files to the ROSSyndicate Google Drive (group f).

To run this pipeline, you will need to have an .Renviron script in your root 
directory (see the readme file for details) and have created a symlink called 'data' 
that accesses B's OneDrive. 

Current settings:
```{r, echo=FALSE}
message("Northern Water and CLP RS pull date: ", Sys.getenv("nw_clp_pull_version_date"))
message("Regional RS pull date: ", Sys.getenv("regional_pull_version_date"))
message("Collation date: ", Sys.getenv("collation_date"))
```

## Install necessary packages

Define package installer function

```{r package_installer}
package_installer <- function(x) {
  if (x %in% installed.packages()) {
    print(paste0("{", x ,"} package is already installed."))
    } else {
      install.packages(x)
      print(paste0("{", x ,"} package has been installed."))
    }
  }
```

List packages that need to be checked for install, and walk the function along them all.

```{r walk_package_installer}
packages <- c("tidyverse",
              "reticulate",
              "targets",
              "tarchetypes",
              "nhdplusTools",
              "polylabelr",
              "sf",
              "readxl",
              "googledrive",
              "feather",
              "cowplot")
lapply(packages, package_installer)
```

## Set up python environment and authenticate EE

```{r}
source("b_RS_data_acquisition/py/pySetup.R")
```

And then authenticate EE. This has to match both your gcloud init settings and your
config settings (especially the project you're running on.)

```{python}
import ee
ee.Authenticate()
```


## Run the targets pipeline and output a network graph.

```{r run_targets}
library(targets)

# run the pipeline
tar_make()

```

### Create a network diagram of the workflow.

```{r}
tar_visnetwork()
```
