---
title: "Run Targets - Northern Water and Cache La Poudre Pipeline"
author: "ROSSyndicate"
---

# Purpose

This script loads all necessary packages to run the {targets} pipeline and then
runs it! This pipeline organizes the location and polygon information for the NW
and CLP projects (group a), pulls and collates the RS pulls for NW and CLP 
reservoirs (group b), pulls and collates RS pulls for all waterbodies in the 
EcoRegion Level 3 Zone 21 AOI, ..., calculates handoff coefficients (group e),
applies handoff coefficients (group f), then separates the NW and CLP data and 
saves the files to the ROSSyndicate Google Drive (group g).

Please see the README in this repository for set up of Earth Engine and gcloud.

Be sure to start a new session before running this file. This markdown is not meant
to be knit.

## Install necessary packages

Define package installer function

```{r package_installer}
package_installer <- function(x) {
  if (x %in% installed.packages()) {
    print(paste0("{", x ,"} package is already installed."))
    } else {
      install.packages(x)
      print(paste0("{", x ,"} package has been installed."))
    }
  }
```

List packages that need to be checked for install, and walk the function along them all.

```{r walk_package_installer}
packages <- c("arrow",
              "cowplot",
              "googledrive",
              "nhdplusTools",
              "polylabelr",
              "readxl",
              "reticulate",
              "sf",
              "targets",
              "tarchetypes",
              "tidyverse")
lapply(packages, package_installer)
```

## Set up python environment and authenticate EE

Check to see if your conda environment is available, otherwise set up a conda 
environment using reticulate.

```{r}
source("pySetup.R")
```

And then authenticate EE. The account you use here has to match both your gcloud 
init settings and your config settings (especially the earth engine project 
you're running on).

```{python}
import ee
ee.Authenticate()
```


## Run the targets pipeline and output a network graph.

At this point, you can run any part of the pipeline. If you run the entire pipeline,
it may take a few hours. At this time, the pipeline will only function through the -c-
group.

```{r run_targets}

library(targets)

# # run the pipeline
# tar_make()

```

### Create a network diagram of the workflow.

```{r}
tar_visnetwork()
```
